\newglossaryentry{twelvefactor}{
    name = 12 Factor App,
    description = {Twelve-factor app is a methodology for building distributed applications that run in the cloud and are delivered as a service.}
}

\newglossaryentry{rails}{
    name = Rails,
    description = {Rails is a full-stack framework. It ships with all the tools needed to build amazing web apps on both the front and back end.}
}

\newglossaryentry{postgresql}{
    name = PostgreSQL,
    description = {PostgreSQL is a powerful, open source object-relational database system with over 35 years of active development that has earned it a strong reputation for reliability, feature robustness, and performance.}
}

\newglossaryentry{heroku}{
    name = Heroku,
    description = {Heroku is a platform as a service (PaaS) that enables developers to build, run, and operate applications entirely in the cloud.}
}

\newglossaryentry{elixir}{
    name = Elixir,
    description = {Elixir is a dynamic, functional language for building scalable and maintainable applications.}
}

\newglossaryentry{rabbitmq}{
    name = RabbitMQ,
    description = {RabbitMQ is a reliable and mature messaging and streaming broker, which is easy to deploy on cloud environments, on-premises, and on your local machine.}
}

\newglossaryentry{docker}{
    name = Docker,
    description = {Docker is an open platform for developing, shipping, and running applications.}
}

\newglossaryentry{arduino}{
    name = Arduino,
    description = {Arduino is an open-source electronics platform based on easy-to-use hardware and software.}
}

\newglossaryentry{rest}{
    name = REST,
    description = {REST, or Representational State Transfer, is an architectural style for providing standards between computer systems on the web, making it easier for systems to communicate with each other.}
}

\newglossaryentry{cnc}{
    name = CNC,
    description={Computer numerical control (CNC) is a manufacturing method that automates the control, movement and precision of machine tools through the use of preprogrammed computer software, which is embedded inside the tools.}
}

\newglossaryentry{sad}
{
    name = SAD,
    description={System Analysis and Design}
}

\newglossaryentry{srs}
{
    name = SRS,
    description={Software Requirements Specification}
}

\newglossaryentry{raspberry_pi}
{
    name = Raspberry Pi,
    description={A small single-board computer developed in the United Kingdom by the Raspberry Pi Foundation}
}

\newglossaryentry{github}
{
    name = GitHub,
    description={A web-based version control system}
}

\newglossaryentry{crud}
{
    name = CRUD,
    description={The four basic operations (create, read, update, and delete) of data storage, regarded collectively.}
}

